### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@def5eea1f0f6197f1f890eb363ef588ef88ad9c2 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4d3855c0d649e889d7d07a7efd382856d0b726a4 🚀

\begin{figure}
\hypertarget{fig:phylo}{%
\centering
\includegraphics{./figures/trees.png}
\caption{Phylogeny for both bumblebee species (left) and flower species
(right)}\label{fig:phylo}
}
\end{figure}

\begin{figure}
\hypertarget{fig:example_sdm}{%
\centering
\includegraphics{./figures/sample_sdm.png}
\caption{Example SDM for \emph{Archillea
millefolium}}\label{fig:example_sdm}
}
\end{figure}

@@

The biggest challenge in implementing simulated annealing in this
context is defining a proposal function for landscape modifications. At
the moment this is done by computing the minimum-spanning-tree (MST) of
the spatial nodes, and then proposing corridors that connect nodes that
are already connected in the MST.

The final component of this chapter is measuring the effect of land-use
change on the robustness of the optimized corridor.

@@

@@

>>>>

@@

\textbf{TK} The biggest challenge in implementing simulated annealing in
this context is defining a proposal function for landscape
modifications. At the moment this is done by computing the
minimum-spanning-tree (MST) of the spatial nodes, and then proposing
corridors that connect nodes that are already connected in the MST.

\textbf{TK} The goal to rank the cells in the raster by priority based
on how many times they are converted in the distribution of ``good''
corridors after simulated annealing has reached a pseudoequilibrium.
Further, the final component of this chapter is measuring the effect of
land-use change on the robustness of the optimized corridor. By
simulating various neutral models of urban and agricultural sprawl, we
can determine if the proposed modifications

@@

\hypertarget{objective-3}{%
\subsection{Objective}\label{objective-3}}

@@

Developing a system for global biodiversity monitoring is an imperative
to mitigate biodiversity loss and its impacts on humanity. In my thesis
I hope to provide a template for the digital infrastructure that enables
the pipeline from data collection, to forecast, to actionable
information, both through software that can be used to solve these
problems (chapters one, three, four), and vignettes of how these
software can be applied (chapters one, two).
